An Algorithm For Spatial Mapping Using a Hexagon Tile Map, With Application to Australian Maps

### 2020-01-18 kobakian_sugarbag_jss/kobakian_sugarbag_jss.Rmd
add angle

---
documentclass: jss
author:
  - name: Stephanie Kobakian
    affiliation: Queensland University of Technology
    address: >
      School of Mathematical Sciences,
      Science and Engineering Faculty,
      Brisbane, QLD, Australia
    email: \email{stephanie.kobakian@qut.edu.au}
  - name: Dianne Cook
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Melbourne, VIC, Australia
    email: \email{dicook@monash.edu}
  - name: Earl Duncan
    affiliation: Queensland University of Technology
    address: >
      School of Mathematical Sciences,
      Science and Engineering Faculty,
      Brisbane, QLD, Australia
    email: \email{earl.duncan@qut.edu.au}
title: 
  formatted: "An Algorithm For Spatial Mapping Using a Hexagon Tile Map, \n With Application to Australian Maps"
  plain: "An Algorithm For Spatial Mapping Using a Hexagon Tile Map, With Application to Australian Maps"
  short: "An Algorithm For Spatial Mapping Using a Hexagon Tile Map"  
abstract: >
  This algorithm creates a tesselated hexagon display to represent each of the spatial polygons. It allocates these hexagon in a manner that preserves the spatial relationship of the geographic units. It showcases spatial distributions, by emphasising the small geographical regions that are often difficult to locate on geographic maps. Spatial distributions have been presented on alternative representations of geography for many years. In modern times, interactivity and animation have begun to play a larger role, as alternative representations have been popularised by online news sites, and atlas websites with a focus on public consumption. Applications are increasingly widespread, especially in the areas of disease mapping, and election results.
keywords:
  # at least one keyword must be supplied
  formatted: [spatial, statistics, cartogram]
preamble: >
  \usepackage{amsmath}
biblio-style: jss
output:
  rticles::jss_article:
    fig_caption: true
    citation_package: natbib
bibliography: sugarbag.bib
link-citations: true
---

@@

# Introduction

@@

# Algorithm

@@

## Parameters

@@

## Polygon set

@@

## Create the set of centroid points

@@

## Create the hexagon grid points

@@

### Step 1: Creating a tesselated grid

@@

### Step 2: Rolling windows

@@

### Step 3: Filtering the grid

@@

## Centroid to focal point distance

@@

## Allocate each centroid to a hexagon grid point

@@

```{r centroids, eval = FALSE}
hexmap_allocation <- allocate(
  centroids = centroids %>% select(SA2_NAME16, longitude, latitude),
  sf_id = "SA2_NAME16",
  hex_grid = grid,
  hex_size = 0.2, # same size used in create_grid
  hex_filter = 10,
  width = 35,
  focal_points = capital_cities,
  verbose = TRUE)
```

@@

### Step 1: Filter the grid for unassigned hexagon points

@@

### Step 2: Filter the grid points for those closest to the centroid

@@

## Neighbour relationships

@@

# Using sugarbag

## Installation

@@

## Creating a hexagon tile map

@@

```{r full_hexmapcode, echo = TRUE, warning = FALSE, message = FALSE, eval=FALSE}
# Load data
data(tas_sa2)

# Create centroids set
centroids <- create_centroids(tas_sa2, "SA2_NAME16")

# Create hexagon grid
grid <- create_grid(centroids = centroids,
    hex_size = 0.2,
    buffer_dist = 1.2)

# Allocate polygon centroids to hexagon grid points
hex_allocated <- allocate(
  centroids = centroids,
  hex_grid = grid,
  sf_id = "SA2_NAME16",
  # same column used in create_centroids
  hex_size = 0.2,
  # same size used in create_grid
  hex_filter = 10,
  use_neighbours = tas_sa2,
  focal_points = capital_cities %>% filter(points == "Hobart"),
  width = 35,
  verbose = FALSE)

# Prepare to plot
fort_hex <- fortify_hexagon(data = hex_allocated, sf_id = "SA2_NAME16", hex_size = 0.2)

# Make a plot
library(ggplot2)
ggplot(fort_hex) + 
  geom_polygon(aes(x=long, y=lat, group=hex_id, fill = lat)) +
  scale_fill_distiller("", palette="PRGn")
```

# Applications

## Australian Cancer Atlas

@@

# Animation

@@

# Conclusion

@@

# Acknowledgements

>>>>

---
documentclass: jss
author:
  - name: Stephanie Kobakian
    affiliation: Queensland University of Technology
    address: >
      School of Mathematical Sciences,
      Science and Engineering Faculty,
      Brisbane, QLD, Australia
    email: \email{stephanie.kobakian@qut.edu.au}
  - name: Dianne Cook
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Melbourne, VIC, Australia
    email: \email{dicook@monash.edu}
  - name: Earl Duncan
    affiliation: Queensland University of Technology
    address: >
      School of Mathematical Sciences,
      Science and Engineering Faculty,
      Brisbane, QLD, Australia
    email: \email{earl.duncan@qut.edu.au}
title: 
  formatted: "An Algorithm For Spatial Mapping Using a Hexagon Tile Map, \n With Application to Australian Maps"
  plain: "An Algorithm For Spatial Mapping Using a Hexagon Tile Map, With Application to Australian Maps"
  short: "An Algorithm For Spatial Mapping Using a Hexagon Tile Map"  
abstract: >
  This algorithm creates a tesselated hexagon display to represent each of the spatial polygons. It allocates these hexagon in a manner that preserves the spatial relationship of the geographic units. It showcases spatial distributions, by emphasising the small geographical regions that are often difficult to locate on geographic maps. Spatial distributions have been presented on alternative representations of geography for many years. In modern times, interactivity and animation have begun to play a larger role, as alternative representations have been popularised by online news sites, and atlas websites with a focus on public consumption. Applications are increasingly widespread, especially in the areas of disease mapping, and election results.
keywords:
  ## at least one keyword must be supplied
  formatted: [spatial, statistics, cartogram]
preamble: >
  \usepackage{amsmath}
biblio-style: jss
output:
  rticles::jss_article:
    fig_caption: true
    citation_package: natbib
bibliography: sugarbag.bib
link-citations: true
---

@@

## Introduction

@@

## Algorithm

@@

#### Parameters

@@

#### Polygon set

@@

#### Create the set of centroid points

@@

#### Create the hexagon grid points

@@

###### Step 1: Creating a tesselated grid

@@

###### Step 2: Rolling windows

@@

###### Step 3: Filtering the grid

@@

#### Centroid to focal point distance

@@

#### Allocate each centroid to a hexagon grid point

@@

```{r centroids, eval = FALSE}
hexmap_allocation <- allocate(
  centroids = centroids %>% select(SA2_NAME16, longitude, latitude),
  sf_id = "SA2_NAME16",
  hex_grid = grid,
  hex_size = 0.2, ## same size used in create_grid
  hex_filter = 10,
  width = 35,
  focal_points = capital_cities,
  verbose = TRUE)
```

@@

###### Step 1: Filter the grid for unassigned hexagon points

@@

###### Step 2: Filter the grid points for those closest to the centroid

@@

#### Neighbour relationships

@@

## Using sugarbag

#### Installation

@@

#### Creating a hexagon tile map

@@

```{r full_hexmapcode, echo = TRUE, warning = FALSE, message = FALSE, eval=FALSE}
## Load data
data(tas_sa2)

## Create centroids set
centroids <- create_centroids(tas_sa2, "SA2_NAME16")

## Create hexagon grid
grid <- create_grid(centroids = centroids,
    hex_size = 0.2,
    buffer_dist = 1.2)

## Allocate polygon centroids to hexagon grid points
hex_allocated <- allocate(
  centroids = centroids,
  hex_grid = grid,
  sf_id = "SA2_NAME16",
  ## same column used in create_centroids
  hex_size = 0.2,
  ## same size used in create_grid
  hex_filter = 10,
  use_neighbours = tas_sa2,
  focal_points = capital_cities %>% filter(points == "Hobart"),
  width = 35,
  verbose = FALSE)

## Prepare to plot
fort_hex <- fortify_hexagon(data = hex_allocated, sf_id = "SA2_NAME16", hex_size = 0.2)

## Make a plot
library(ggplot2)
ggplot(fort_hex) + 
  geom_polygon(aes(x=long, y=lat, group=hex_id, fill = lat)) +
  scale_fill_distiller("", palette="PRGn")
```

## Applications

#### Australian Cancer Atlas

@@

## Animation

@@

## Conclusion

@@

## Acknowledgements
